FictionEro - Affective Impact of Fiction

### 2025-11-11 analysis/analysis.qmd
minor

@@

g1 <- modelbased::estimate_grouplevel(model_draft)
table_dvour(g1)

@@

p2_dvour <- g1 |> 
  ggplot(aes(x = Coefficient, y = Level)) +
  geom_pointrange(aes(xmin = CI_low, xmax = CI_high, color = Parameter), linewidth = 0.3, size = 0.05) +
  facet_grid(Group~Parameter, scales = "free", switch="both") +
  ggside::ggside(scales  = "free") +
  ggside::geom_xsidedensity(aes(group = Parameter, fill = Parameter), color = NA) +
  ggside::ggside(scales  = "free") +
  scale_color_manual(values = colors) +
  scale_fill_manual(values = colors) +
  theme_minimal() +
  theme(axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        strip.placement.x = "outside",
        strip.background = element_rect(fill = NA, color = NA),
        axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        panel.grid.minor = element_blank(),
        panel.grid.major.y = element_blank(),
        legend.position = "none")
p2_dvour
```

>>>>

<!-- These functions provide information about the reliability of group-level estimates (i.e., random effects) in mixed models. They are useful to assess whether the predictors yield consistent group-level variability. "Group-level" can refer, for instance, to different participants in a study, and the predictors to the effect of some experimental condition. -->

<!-- D_vour: corresponds to the normalized ratio of observed variability to uncertainty in random effect estimates -->

@@

draft_model <- brms::brm(
  formula = Arousal ~ Gender / (Condition * ConditionBelief) + (1  + Condition | Participant) + (1|Item),
  data = df2,
  family = brms::zero_one_inflated_beta())

g1 <- modelbased::estimate_grouplevel(arousal2)
table_dvour(g1)

@@

p2_dvour <- g1 |> 
  ggplot(aes(x = Estimate, y = Level)) +
  geom_pointrange(aes(xmin = CI_low, xmax = CI_high, color = Parameter), linewidth = 0.3, size = 0.05) +
  facet_grid(Group~Parameter, scales = "free", switch="both") +
  ggside::ggside(scales  = "free") +
  ggside::geom_xsidedensity(aes(group = Parameter, fill = Parameter), color = NA) +
  ggside::ggside(scales  = "free") +
  scale_color_manual(values = colors) +
  scale_fill_manual(values = colors) +
  theme_minimal() +
  theme(axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        strip.placement.x = "outside",
        strip.background = element_rect(fill = NA, color = NA),
        axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        panel.grid.minor = element_blank(),
        panel.grid.major.y = element_blank(),
        legend.position = "none")
p2_dvour
```
